---
title: "belief-prior-exp"
author: "mht"
date: "September 8, 2014"
output: html_document
---
```{r setup, echo=FALSE}
agr.ci <- function(x){
  agr = aggregate(value ~ domain + condition + variable, data=x, FUN=mean)
  agr$CILow = aggregate(value ~ domain + condition + variable, data=x, FUN=ci.low)$value
  agr$CIHigh = aggregate(value ~ domain + condition + variable, data=x, FUN=ci.high)$value
  agr$YMin = agr$value - agr$CILow
  agr$YMax = agr$value + agr$CIHigh
  return(agr)
}
```
This report looks at the data elicited from 03syllogism-prior-exp. We asked people about the plausibility or frequency of various combinations of objects occurring. This is the so-called *prior elicitation* part of the experiment. 

Let's start with the RT distribution. This is the time to complete the 8-state multinomial elicitation. 

```{r}
fpath = '/Users/mht/Documents/research/syllogism/data/03syllogism_prior_psychjs/'

df<-read.csv((paste(fpath,'prior-exp-mturk_all_n71.csv',sep="")))[c(1:12,16)]
df$condition<-factor(df$condition,labels=c('plausibility','frequency'))

ggplot(df, aes(x=(rt/1000)))+
  geom_histogram(binwidth=1)+
  theme_bw()+
  ggtitle("time to complete item (RTs), binsize = 1s")+
  xlab('time (sec)')+
  ylab('number of items')

#df<-subset(df,rt<500000)

ggplot(df, aes(x=(rt/1000),fill=condition))+
  geom_histogram(binwidth=3)+
  theme_bw()+
  facet_wrap(~condition)+
  ggtitle("time to complete item (RTs), binsize = 3s")+
  xlab('time (sec)')+
  ylab('number of items')
```

Looks like one person fell asleep in the chair. Otherwise, normalish around 50seconds per 8 state elicitation. Reasonable.

### raw slider value distribution

```{r}
ggplot(melt(df[3:11]), aes(x=value,fill=condition))+
  geom_histogram(binwidth=10)+
  facet_wrap(~condition)+
  theme_bw()+
  ggtitle('raw slider values')+
  xlab('slider value, binsize = 10')+
  ylab('number of responses')


property_labels <- c('Q_XYZ','Q_XYnZ','Q_XnYZ','Q_nXYZ','Q_XnYnZ','Q_nXYnZ','Q_nXnYZ','Q_nXnYnZ')

df$sum<-rowSums(df[,property_labels])
df$max<-apply(df[,property_labels],1,max)

ggplot(melt(df[c('condition','max')]), aes(x=value,fill=condition))+
  geom_histogram(binwidth=5)+
  facet_wrap(~condition)+
  theme_bw()+
  ggtitle('max raw slider values')+
  xlab('slider value, binsize = 5')+
  ylab('number of responses')

```

[with n=29 for plausibility and n=21 for frequency] 
the frequency distribution appears exponential while the plausibility distribution appears uniform. There are many more 0 responses for the frequency prompt. This in unnormalized data remember.

### Raw sum distributions
```{r}
ggplot(melt(df[c('condition','sum')]), aes(x=value,fill=condition))+
  geom_histogram(binwidth=10)+
  facet_wrap(~condition)+
  theme_bw()+
  ggtitle('Sum of slider values')+
  xlab('slider value, binsize = 10')+
  ylab('number of responses')
```

Raw sums of plausibility elicitations are normalish around 400. This is (by coincidence?) 8 (state) * 100 / 2, fyi.

Frequency doesn't show this. Instead, we get a great number which sum to approximately 100, and others that go beyond.

**mini-hypothesis: the sum=100 responses occur when max response is near 100, i.e. when the 8-state is {100, 0, 0, 0, 0, 0, 0, 0}.** We're going to plot the max response vs. the sum of responses, for each item.

```{r}


ggplot(df[c('condition','sum','max')],aes(x=sum,y=max,color=condition))+
  geom_point(alpha=0.8,position=position_jitter(10))+
  facet_wrap(~condition)+
  theme_bw()

ggplot(subset(df,sum<120),aes(x=max))+
  geom_histogram(binwidth=2)+
  facet_wrap(~condition)+
  theme_bw()+
  ggtitle('distribution of max slide val for sum(slider) < 120')

```

This plot must reside above the y=x line. The only thing I take away from this is that there are many points in the top left corner for the frequency judgments, supporting the mini-hypothesis above.

### normalized slider value distribution

```{r}
df_norm = ddply(df, .(domain, condition), function(x) {
  means = x[,c('Q_XYZ','Q_XYnZ','Q_XnYZ','Q_nXYZ','Q_XnYnZ','Q_nXYnZ','Q_nXnYZ','Q_nXnYnZ')]
  means / rowSums(means)
})

df_norm$max<-apply(df_norm[,property_labels],1,max)

ggplot(df_norm,aes(x=max,fill=condition))+
  geom_histogram(binwidth=0.02,aes(y=..count../sum(..count..)))+
  facet_wrap(~condition)+
  theme_black()+
  xlab("\nMaximum (normalized) slider value")+
  ylab("Proportion of responses\n")+
  #ggtitle('distribution of max slide val for normalized values')+
  theme(strip.text= element_text(size=30),
     #   plot.title= element_text(size=),
        axis.title=element_text(size=32),
        axis.text=element_text(size=25))+
  guides(fill=FALSE)#guide_legend(title=NULL))

df_norm<- df_norm[,-11]

ggplot(melt(df_norm), aes(x=value,fill=condition))+
  geom_histogram(binwidth=0.1)+
  facet_wrap(~condition)+
  theme_bw()+
  ggtitle('normalized slider values')+
  xlab('slider value, binsize = 0.1')+
  ylab('number of responses')

ggplot(melt(df_norm), aes(x=value,fill=condition))+
  geom_histogram(binwidth=0.01)+
  facet_wrap(~condition)+
  theme_bw()+
  ggtitle('normalized slider values')+
  xlab('slider value, binsize = 0.01')+
  ylab('number of responses')
```

[with n=29 for plausibility and n=21 for frequency] 
both distributinos look exponential, but frequency has more in the tail than plausibility, which really doesn't go above 0.4

This note holds for n's = 35. Frequency is mostly strictly decreasing, while plausibility avoids the "impossible" endpoint.

### 8-state multinomial elicitation

```{r, fig.width=16, fig.height=8}

#df_norm$max<-apply(df_norm[,property_labels],1,max)
#df_norm<-subset(df_norm,max<0.95)
#df_norm<- df_norm[,-11]

ci_bs <- agr.ci(melt(df_norm))
ci_bs$domain<-factor(ci_bs$domain,
                     levels=c('lightbulb','tomatoplant','strawberry',
                              'cracker','knife','painting'))
ci_bs$variable<-factor(ci_bs$variable,
                       levels=c('Q_nXnYnZ','Q_XnYnZ','Q_nXYnZ',
                                'Q_nXnYZ','Q_XYnZ','Q_XnYZ','Q_nXYZ',
                                'Q_XYZ'))

mean_cast <-dcast(ci_bs[,1:4], value.var='value',...~condition)
with(mean_cast,cor(frequency,plausibility))

ggplot(mean_cast,aes(x=frequency,y=plausibility,color=domain))+
geom_point(size=4)+
  theme_bw()+
  xlim(0,0.4)+
  ylim(0,0.4)

ggplot(ci_bs, aes(x=variable, y=value, fill=condition)) + 
  geom_bar(position=position_dodge(.6), stat='identity')+
    geom_errorbar(aes(ymin=YMin,ymax=YMax),width=0.5,alpha=0.6,
                position=position_dodge(.6))+
  xlab("property set")+
  ylab("rating")+
  facet_grid(condition~domain)+
  ggtitle("priors")+
  theme_bw()+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=.5,colour='gray50'),
    strip.text.x = element_text(size=20),
    strip.text.y = element_text(size=24,angle=270))
```

NOTE: Properties on the X-axis are arranged from Absence of all properties (Left) to Presence of all proeprties (Right)

### dot plot

```{r, fig.width=16, fig.height=24}

df_nmelt<-melt(df_norm)

df_nmelt$variable<-factor(df_nmelt$variable,
                          levels=c('Q_nXnYnZ','Q_XnYnZ','Q_nXYnZ',
                                'Q_nXnYZ','Q_XYnZ','Q_XnYZ','Q_nXYZ',
                                'Q_XYZ'))

df_nmelt$domain<-factor(df_nmelt$domain,
                     levels=c('lightbulb','tomatoplant','strawberry',
                              'cracker','knife','painting'))


ggplot(df_nmelt, aes(x=variable, y=value, colour=condition, fill=condition))+
  geom_dotplot(binaxis = "y", binwidth=.03, dotsize=1)+
  xlab("property set")+
  ylab("rating")+
  facet_grid(domain~condition)+
  ggtitle("priors")+
  theme_bw()+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=.5,colour='gray50'),    strip.text.x = element_text(size=20),
    strip.text.y = element_text(size=24,angle=270))
```

-----
Literal models using frequency and plausibility.

```{r}
# Load model predictions, for different parameter (n_object) values
model.dir<-'/Users/mht/Documents/research/syllogism/models/modeldata/LATTICE_4_'

syllogisms = c('AO2', 'EA3', 'IE1', 'OA1','AA1','AI1','EA1','EI1')

if (exists('models')){remove(models)}
EP = 1
n_obj=6
  model.domains = data.frame()
domains<-c("cracker","knife","lightbulb","strawberry")
conditions<-c("plausibility","frequency")

for (cond in conditions){
for (d in domains){
    model.all<-read.csv(paste(model.dir,cond,'/00/csv/lis_N0_M0_',cond,
                              d,'_qud1figFull_AIEOc4CAEP',EP,'_n',n_obj,
                              '_base0.00_s100k_alphQ1_alphR1.csv',sep=''))[c(1,6:9)]
    #model.sub<-model.all[model.all$X..syll%in%syllogisms,]
    model.sub<-model.all
    model.sub$domain <- d
    model.sub$cond<- cond
    model.m<-melt(model.sub,
                  id.vars=c('X..syll','domain','cond'))
    model.domains<-rbind(model.domains, model.m)
  }
}
mod.cast<-dcast(model.domains, value.var='value',...~cond)
with(mod.cast,cor(frequency,plausibility))
```

-----
Pragmatics models using frequency and plausibility.

```{r}
# Load model predictions, for different parameter (n_object) values
model.dir<-'/Users/mht/Documents/research/syllogism/models/modeldata/LATTICE_4_'

syllogisms = c('AO2', 'EA3', 'IE1', 'OA1','AA1','AI1','EA1','EI1')

if (exists('models')){remove(models)}
EP = 1
n_obj= 6
alpha = 3
  model.domains = data.frame()
domains<-c("cracker","knife","lightbulb","strawberry")
conditions<-c("plausibility","frequency")

for (cond in conditions){
for (d in domains){
    model.all<-read.csv(paste(model.dir,cond,'/10/csv/lis_N1_M0_',cond,
                              d,'_qud1figFull_AIEOc4CAEP',EP,'_n',n_obj,
                              '_base0.00_s100k_alphQ',alpha,'_alphR1.csv',sep=''))[c(1,6:9)]
    #model.sub<-model.all[model.all$X..syll%in%syllogisms,]
    model.sub<-model.all
    model.sub$domain <- d
    model.sub$cond<- cond
    model.m<-melt(model.sub,
                  id.vars=c('X..syll','domain','cond'))
    model.domains<-rbind(model.domains, model.m)
  }
}
mod.cast<-dcast(model.domains, value.var='value',...~cond)
with(mod.cast,cor(frequency,plausibility))
with(subset(mod.cast,X..syll%in%syllogisms),cor(frequency,plausibility))

ggplot(data=subset(model.domains,X..syll%in%syllogisms), aes(x=variable,y=value,fill=cond))+
  geom_bar(stat='identity',position=position_dodge())+
  theme_black()+
  facet_grid(domain~X..syll)
```




----
OED stuff

```{r, kl plots,fig.width=10,fig.height=6,echo=TRUE}
fpath<-'/Users/mht/Documents/research/syllogism/data/03syllogism_prior_psychjs/'
oeds<-list.files(fpath,pattern='oed.*\\.txt')

oed.res = data.frame(syll=rep(NA,0),prior=rep(NA,0),
                        kl=rep(NA,0),valid=rep(NA,0),
                        stringsAsFactors=FALSE)

valid.ca <- read.table('/Users/mht/Documents/research/syllogism/models/metadata/allvalidmoodsCA.txt',header=TRUE)

for (o in oeds){
  df.tm <- read.table(paste(fpath,o,sep=''),col.names=c('syll','kl'))
  df.tm$valid<-df.tm$syll%in%valid.ca$syll
  df.tm$prior<-substr(o,5,12)
  df.tm$syll<- factor(df.tm$syll,levels=df.tm$syll[order(df.tm$kl)])
  oed.res<-rbind(oed.res,df.tm)
}


oed.res$syll = as.character(oed.res$syll)
oed.res$n = as.numeric(factor(oed.res$prior))

oed.res = ddply(oed.res, .(syll,valid,prior), transform,
                x=paste(c(rep(' ',n-1), syll), collapse=''))

oed.res$x = factor(oed.res$x, levels=oed.res[order(-oed.res$kl), 'x'])

ggplot(data=oed.res,aes(x=x,y=kl,fill=valid))+
  geom_bar(stat='identity')+
  facet_wrap(~prior,scale='free_x')+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=.5,colour='gray50'))

ggplot(data=subset(oed.res,prior='frequenc'),aes(x=x,y=kl,fill=valid))+
  geom_bar(stat='identity')+
  theme_bw()+
  xlab("syllogism (experiment)")+
  ylab("expected KL")+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=.5,colour='gray50'))
```

Good to see that these basically look the same.



```{r,predicition plots, fig.width=9,echo=FALSE}
#oed.res,!valid & 
library(stringr)

substrRight <- function(x, n){
  substr(x, nchar(x)-n+1, nchar(x))
}

toonec<-c("AE4","AA1","EA1","AE2","EA2")

oed.ccee<-subset(oed.res, !(syll%in%toonec) & prior=='plausibi')

top16<-oed.ccee[order(-oed.ccee$kl)[seq(1,16,1)],]
topchoice<-top16[seq(1,16,4),]
topchoice<-top16[c(1,2,3,5,10,12,13),]
fpath<-'/Users/mht/Documents/research/syllogism/data/03syllogism_prior_psychjs/'
m.df<-read.csv(paste(fpath,'3modeldata_oed_plausibility_depth0iidArgStr_emprArgStr_emprCLonly.csv',sep=''))[-1]

m.df<-subset(m.df,X..syll%in%topchoice$syll)
mm.df<-melt(m.df,id.vars=c('model','X..syll'))
mm.df$response<-as.character(mm.df$variable)

mm.df$domain<-str_split_fixed(mm.df$response, "[.]", 2)[,1]
mm.df$conclusion<-str_split_fixed(mm.df$response, "[.]", 2)[,2]

ggplot(data=subset(mm.df,substrRight(as.character(variable),3)%in%c("Isp","Osp")),aes(x=conclusion,y=value))+
  geom_bar(aes(fill=model),stat='identity',position='dodge')+
  facet_grid(domain~X..syll)+
scale_alpha_manual(values=c(1,0.5))+
  #scale_x_discrete(labels=c("some C are A","some C are not A"))+
  theme_bw()+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=.5,colour='gray50'))




```

```{r}

a<-subset(mm.df,(model%in%c('argstr_empr','clonly_empr') & (dom=='cracker')))



ggplot(data=subset(a,X..syll%in%c('AA1','II1')),aes(x=conclusion,y=value))+
  geom_bar(aes(fill=model),stat='identity',position='dodge')+
  facet_wrap(~X..syll)+
scale_alpha_manual(values=c(1,0.5))+
  ylab('predicted response')+
  scale_x_discrete(labels=c("All C are A","No C are A","some C are A","some C are not A"))+
  theme_bw()+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=.5,colour='gray50'))


```
































