---
title: "syllogisms"
author: "mht"
date: "October 21, 2015"
output: html_document
---



```{r helders}
library(coda)
library(purrr)
estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
HPDhi<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
HPDlo<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
options("scipen"=10)   
```


# Human data from existing data sets

### Rips (1994) Data

```{r data.load}
d<-read.csv("~/Documents/research/syllogism/models/ripsdata/rips-data-raw-boolean.csv")

d.tidy <- d %>% 
  group_by(syllogism, conclusion) %>%
  multi_boot_standard(column="response")


qplot(data=d.tidy, x = mean, geom='histogram')

```

Rips told participants that valid things would only occur on 10% of trials.

### Evans et al. (1999) Data

```{r data.load}
e<-read.csv("~/Documents/research/syllogism/models/ripsdata/evans-data-raw-boolean.csv")

e.tidy <- e %>% 
  group_by(syllogism, conclusion) %>%
  multi_boot_standard(column="response")
qplot(data=e.tidy, x = mean, geom='histogram')

```

Told participants to that the conclusion had to necessary follow form the premises.

### Comaparison of Rips and Evans

```{r}
de.joined<- left_join(
              d.tidy %>%
                rename(ripsMean = mean,
                       ripsLower = ci_lower,
                       ripsUpper = ci_upper),
              e.tidy %>%
                rename(evansMean = mean,
                       evansLower = ci_lower,
                       evansUpper = ci_upper)
)

ggplot(de.joined, aes(x=ripsMean, y=evansMean, color=conclusion))+
  geom_point()+
 # geom_errorbar(aes(ymin=evansLower, ymax=evansUpper))+
 # geom_errorbarh(aes(xmin=ripsLower, xmax = ripsUpper))+
  scale_color_solarized()

with(de.joined, cor(ripsMean, evansMean))
```

### Closer look at Evans et al. (1999)

How different are the structural forms?

```{r evans.byFigure}

#evans data
e.tidy %>%
  separate(syllogism, sep = 2, into = c("premises", "figure")) %>%
  select(-ci_lower, -ci_upper) %>%
  spread(figure, mean) %>%
  ggcorplot()

#rips data
d.tidy %>%
  separate(syllogism, sep = 2, into = c("premises", "figure")) %>%
  select(-ci_lower, -ci_upper) %>%
  spread(figure, mean) %>%
  ggcorplot()
```


# Human data from FYP data sets

### Prior elicitation experiment

Here, I'm looking at the prior elicitation data, but I'm not sure I have decoded the randomization scheme properly.

```{r data.fyp.prior}
fyp.prior<- read.csv("~/Documents/research/syllogism/data/02syllogism-1ca/syllogism02_priors.csv")

pr.tidy<-fyp.prior %>% 
  select(-subj,-time, -language,-age,-gender,-logic,-browser, -comments, -X) %>%
  gather(prop, response, starts_with("X")) 


pr.stats<- pr.tidy %>%
  group_by(matId, prop) %>%
  multi_boot_standard(column="response")

ggplot(pr.stats,aes(x=prop, y = mean))+
  geom_bar(stat='identity', position=position_dodge())+
  geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper))+
  facet_wrap(~matId)
```


Here, I'm looking at this data set collapsing across content (which was very strongly randomized that I'm not sure I can decode it).

```{r data.fyp.1}

fyp.data<- read.csv("~/Documents/research/syllogism/data/02syllogism-1ca/syllogism02-1_conclusions.csv")

fyp.data<-fyp.data %>% 
  unite(SMP, S, M, P)

fyp.tidy <- fyp.data %>%
  select(syll, matId, Asp, Esp, Isp, Osp, SMP) %>%
  gather(conclusion, response, Asp, Esp, Isp, Osp) %>%
  group_by(syll, conclusion) %>%
  multi_boot_standard(column='response') %>%
  mutate(conclusion = factor(conclusion, 
                             levels=c("Asp", "Isp", "Esp", "Osp"),
                             labels=c("all", "some", "none","not all"))) %>%
  rename(syllogism = syll)
  

fyp.evans.joined<- left_join(
              fyp.tidy %>%
                rename(fypMean = mean,
                       fypLower = ci_lower,
                       fypUpper = ci_upper),
              e.tidy %>%
                rename(evansMean = mean,
                       evansLower = ci_lower,
                       evansUpper = ci_upper)
)

ggplot(fyp.evans.joined, aes(x=fypMean, y=evansMean, color=conclusion))+
  geom_point()+
  geom_errorbar(aes(ymin=evansLower, ymax=evansUpper))+
  geom_errorbarh(aes(xmin=fypLower, xmax = fypUpper))+
  geom_abline(intercept=0, slope=1)+
  scale_color_solarized()+
  xlim(0,1)+
  ylim(0,1)+
  coord_fixed()

with(fyp.evans.joined, cor(fypMean, evansMean))

```


# Model

```{r model.load}
fpath<- "~/Documents/research/syllogism/models/results/"
prefix<- "rips-bySyllogism-nObj4-br-phi-MH"
prefix<- "rips-bySyllogism-pragProd-qudcL0premises_nObj4-br-phi-MH"
prefix<- "rips-bySyllogism-pragProd-qudcL0premises_nObj4-br-phi-MH"
prefix<- "rips-bySyllogism-pragInt-qudE1conclusion_nObj4-br-phi-MH"
prefix<- "rips-byConclusion-16alts-pragInt-qudE1conclusion_nObj4-br-phi-MH"
prefix<- "rips-byConclusion-16alts-pragProd-qudcL0premises_nObj4-br-phi-cost-MH"
prefix<- "evansData-conclusionPairs-pragProd-qudcL0premises_nObj4-phi-costMH"
samples = 100
burn = samples /2
m<-read.csv(paste(fpath, prefix, samples, "burn", burn,".csv", sep=''))
m.samples <- m[rep(row.names(m), m$Probability*samples), 1:5]
```


# Posterior over parameters

```{r posterior.parameters}

m.params <- m.samples %>%
  filter(Type=='parameter')

ggplot(m.params, aes(x=Value))+
  geom_histogram()+
  facet_wrap(~Parameter, scales='free')

```

# Posterior predictive

```{r posterior.predictives}

m.pp <- m.samples %>%
  filter(Type == 'predictive') %>%
  group_by(Parameter, Item) %>%
  summarize(MAP = estimate_mode(Value),
            credHigh = HPDhi(Value),
            credLow = HPDlo(Value)) %>%
  rename(syllogism = Parameter,
         conclusion=Item)


m.d <-left_join( m.pp,e.tidy)


with(m.d, cor(mean, MAP))

ggplot(m.d, aes(x=MAP, y = mean, color=conclusion))+
  geom_point()+
  coord_fixed()+
  xlim(0.05,1.05)+
  ylim(0.05,1.05)+
  geom_errorbarh(aes(xmin=credLow, xmax=credHigh))
#+
# geom_errorbar(aes(ymin=ci_lower, ymax = ci_upper))
```

